Analysis

### 2019-11-29 analysis.Rmd
update missings & graphs

table_perob$ocup <- c("Obrero")
table_perob$year <- c(1999,2009,2019)

table_perger$ocup <- c("Gerente")
table_perger$year <- c(1999,2009,2019)

table_pertot <-rbind(table_perger,table_perob)
table_pertot

ggplot(table_pertot, aes(as.factor(year), median)) +
      geom_bar(aes(fill = ocup), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Salario (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ") # quitar nombre leyenda, autoexplicativo

>>>>

table_perob$ocup <-  1 # as.factor(c("Obrero"))
table_perob$year <- c(1999,2009,2019)

table_perger$ocup <- 2 # as.factor(c("Gerente"))
table_perger$year <- c(1999,2009,2019)

table_pertot <-rbind(table_perger,table_perob)
str(table_pertot)
table_pertot

ggplot(table_pertot, aes(as.factor(year), median)) +
      geom_bar(aes(fill = factor(ocup, levels=c(1,2), labels=c("Obrero", "Gerente"))), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Salario (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ")

+ # quitar nombre leyenda, autoexplicativo +

      coord_flip()
